Mixed effect tweedie model in TMB

### 2019-07-17 analysis/tmb-sensor-explore/3-fit-do.Rmd
minor organizational edits

```{r setup}
library(tidyverse)
library(gfplot)
library(sdmTMB)
library(gfranges)

#library(future)
#library(dplyr)

# plan(multiprocess)
```

@@

```{r}
# # filter surveys if desired
# d_trawl <- d_trawl %>% 
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  # remove obvious sensor fails, d_trawl %>% filter(depth_max<10), fishing event ids = 481861, 2179089
  # filter(depth_m_max>10) %>%

@@

    do_model_re_DOY <- sdmTMB::sdmTMB(d_trawl1,
      log_do ~ 0 + as.factor(year) + temp_scaled + temp_scaled2 ,
      time_varying = ~ 0 + DOY_scaled + depth_scaled + depth_scaled2 + depth_scaled3,
      time = "year", spde = spde,
      family = gaussian(link = "identity"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = FALSE,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime1 <- Sys.time()
    time1 <- round(starttime1 - endtime1)

saveRDS(do_model_re_DOY, file = (here::here("analysis/tmb-sensor-explore/models/model-do-re-DOY.rds")))
time1
do_model_re_DOY
```

```{r}
do_model_re_DOY <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-do-re-DOY.rds"))
do_model_re_DOY
```

```{r}
get_diag(do_model_all_fe, response = "log_do", variable = "depth_scaled")

@@

@@

plot_map_raster(p_nd, "do_est") +
  scale_fill_viridis_c(trans = "log") +
  facet_wrap(~year) +
  ggtitle("Prediction (fixed effects + all random effects)")

>>>>

```{r setup}
library(tidyverse)
library(gfplot)
library(sdmTMB)
library(gfranges)
```

@@

```{r}
# # filter surveys if desired
# d_trawl <- d_trawl %>% 
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  # remove obvious sensor fails, d_trawl %>% filter(depth_max<10), fishing event ids = 481861, 2179089
  # filter(depth_m_max>10) %>% 
```

@@

    do_model_all_DOY <- sdmTMB::sdmTMB(d_trawl1,
      log_do ~ 0 + as.factor(year) + temp_scaled + temp_scaled2 + DOY_scaled,
      time_varying = ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
      time = "year", spde = spde,
      family = gaussian(link = "identity"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = FALSE,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime1 <- Sys.time()
    time1 <- round(starttime1 - endtime1)

saveRDS(do_model_all_DOY, file = (here::here("analysis/tmb-sensor-explore/models/model-do-all-DOY2.rds")))
time1
do_model_all_DOY
```

@@

```{r eval=FALSE}
#with both DOY and depth as time-varying random effects
do_model_re_DOY <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-do-re-DOY.rds"))
do_model_re_DOY
get_diag(do_model_re_DOY, response = "log_do", variable = "depth_scaled")
```

@@

plot_map_raster(p_nd, "do_est") +
  scale_fill_viridis_c(trans = "log") +
  facet_wrap(~year) +
  ggtitle("Prediction (fixed effects + all random effects)")
```
